Reading Notes

### 2020-08-18 2pd.tex
fixed close }
good stopping point for md -- v rough

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/bondangledihedral.pdf}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image taken from \cite{punma}.
    \label{fig:bad}
\end{wrapfigure}

$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
The angle potential is also treated as a harmonic oscillator:
$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
The dihedral potential can be defined by the follow Fourier series:
$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.

The first MD simulation modelled a system of 108 particles, and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
Now GPUs are 100 millions times faster
%%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
protein folding \cite{levitt75}, other biological processes, polymers \cite{Gartner2019a}

%%<what assumptions does md make?>
bonds aren't formed or broken, electrons don't exist
hydrogen bonding
dispersion is tricky--electrons don't slosh around unless you use some fancy many-body potential
%%<what are the limits of atomistic md?>
%%<segue to why we need CG models>

>>>>

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.4\linewidth]{images/bondangledihedral.pdf}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
    \label{fig:bad}
\end{wrapfigure}

$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
The angle potential is also treated as a harmonic oscillator:
$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
The dihedral potential can be defined by the follow Fourier series:
$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
Where $\phi$ is the angle between planes formed by particles in the dihedral (see Figure \ref{fig:bad}) and $k_{n}$ are the force coeffients.
%% transition???
The first MD simulation modelled a system of 108 particles, and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
Now GPUs are 100 millions times faster.
%%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
Due to its efficient scaling, MD is now commonly used for modelling of protein folding \cite{levitt75} and other biological processes, and investigating the bulk properties of polymers \cite{Gartner2019a}.

%%<what assumptions does md make?>
Even all-atom MD is not without assumptions:
In general, during an MD simulation bonds aren't formed or broken, so without careful consideration this prevents the study of chemical reactions.
MD does not consider electrons, instead atoms are treated as point particles. 
This makes modelling systems which depend on hydrogen bonding or dispersion more difficult.

%%<what are the limits of atomistic md?>
Even with these simplifications, we are still not able to simulate many systems efficiently on relevant length scales.
Therefore we can use a technique called coarse graining to increase the length and time scale we can examine.
%%<segue to why we need CG models>
